---
title: "Analysis On Number Of Policies Owned By policyholders"
output: 
  html_document:
      toc: true
      toc_float: 
        smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10)
```

```{r message=FALSE, include=FALSE, results='hide'}
source("lab_data.R", local = knitr::knit_global())
source("eda_functions.R", local = knitr::knit_global())
```
<br>

### Number of policies with total claim amount
```{r}
data_np <- data %>% 
  select(number_of_policies, total_claim_amount) %>% 
  mutate(number_of_policies = as.character(number_of_policies))

num_cat_sumy(data_np, total_claim_amount, number_of_policies, sumy_fun = sum)

corr_lysis(data, number_of_policies, total_claim_amount)
```
  
The number of policies does not have a positive relationship with the total
amount claimed by policyholders.
  
<br>

### Number of policy and the Number of open complains by customers
##### Count of open complain
```{r}
data %>% 
  mutate(number_of_open_complaints = as.character(number_of_open_complaints)) %>% 
  count_obs(number_of_open_complaints)
```
  
Few customers made more than 2 complains about the company products and services. 
  
```{r}
data %>% 
  group_by(number_of_policies, number_of_open_complaints) %>% 
  count(name = "count") %>% 
  ungroup() %>%
  
  ggplot(aes(factor(number_of_policies), count)) +
  geom_col(fill = "#42b395") +
  facet_wrap(vars(number_of_open_complaints), ncol = 3, scales = "free_y") +
  theme_minimal() +
  labs(x = "Number Of Policies", y = "Count", 
       title = "Count of Number of Policy By Number of Open Complain")
```
  
##### Percentage of complains made by number of policy owned
```{r}
data %>% 
  group_by(number_of_policies, number_of_open_complaints) %>% 
  count(name = "count") %>% 
  ungroup() %>% 
  left_join(count(data, number_of_policies), by = "number_of_policies") %>% 
  mutate(prop = count/n*100) %>% 
  select(-c(count, n)) %>% 
  pivot_wider(number_of_policies, 
              names_from = number_of_open_complaints, 
              values_from = prop, values_fill = 0)
```

A lager number of customers for all numbers of policy owned made zero complains.
  
<br>

### Relationship between number of policy owned and policy type
```{r}
data %>% 
  count(number_of_policies, policy_type, name = "count") %>% 
  
  ggplot(aes(count, 
             reorder_within(factor(number_of_policies), count, policy_type))) +
  geom_col(fill = "#42b395") +
  facet_wrap(vars(policy_type), scales = "free", ncol = 3) +
  scale_y_reordered() +
  labs(y = "Number Of Policy", 
       title = "Count of Number of Policy By Policy Type") +
  geom_text(aes(label = count), hjust = 1.0) +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())
```
  
For each type of policy, customers with 1 to 3 policies at most have the 
highest number of customers. Special auto have the least number of customers for each number of policy. Also customers with 6 policies have the lowest count for corporate and personal auto policy types.
  
<br>
Previous [Various Features Used In Determining Auto Premium](page_2.html)  
Next [Sales Channels And Vehicle Classification](page_4.html)