---
title: "Various Features Used In Determining Auto Premium"
output: 
  html_document:
      toc: true
      toc_float: 
        smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10)
```

```{r message=FALSE, include=FALSE, results='hide'}
source("lab_data.R", local = knitr::knit_global())
source("eda_functions.R", local = knitr::knit_global())
```
<br>

### Relationship between total claim amount and Premium

##### Correlation
```{r}
corr_lysis(data, monthly_premium_auto, total_claim_amount)
```
  
```{r}
numerical_rel(data,
              monthly_premium_auto,
              total_claim_amount, p_typ = "bin2d")
```
  
There is a moderate positive correlation (0.632) between the total amount 
claimed by customers and the amount of premium paid on a monthly basis. There is a large number of customers that have less than 500 claim amount pays less than 80 premium monthly.
  
<br>

### Relationship between coverage and Premium
```{r}
num_cat_dis(data, monthly_premium_auto, coverage)

num_cat_sumy(data, monthly_premium_auto, coverage)

num_cat_sumy(data, monthly_premium_auto, coverage, sumy_fun = sum)
```

The higher the level of coverage the more the average monthly premium that
was paid.
  
<br>

### Relationship between driver profile and Premium
##### Marital status
```{r}
num_cat_sumy(data, monthly_premium_auto, marital_status)
```
  
There is a slight distinction in the median premium paid monthly between 
married (83.0), Single (82.0) and Divorced (81.0) customers.
  
##### Gender
```{r}
num_cat_dis(data, monthly_premium_auto, gender, p_typ = "fqp")
num_cat_sumy(data, monthly_premium_auto, gender, sumy_fun = sum)
```
  
Female customers paid more premium (433,600) than male customers (417,865) but
on an average there is a little difference in the amount of premium paid.
  

```{r, fig.width=10}
num_cat_sumy2(data, monthly_premium_auto, marital_status, gender)

g_ms <- data %>% 
  group_by(marital_status, gender) %>% 
  numeric_summary(monthly_premium_auto)

g_ms_f <- filter(g_ms, gender == "Female")
g_ms_m <- filter(g_ms, gender == "Male")
  
ggplot(g_ms, aes(y = marital_status, fill = gender)) +
  geom_col(data = g_ms_f, aes(x = sum), color = "white") +
  geom_col(data = g_ms_m, aes(x = -1*sum), color = "white") +
  geom_text(data= g_ms_f, aes(label=scales::comma(sum), x=sum), hjust= 1.3) +
  geom_text(data= g_ms_m, aes(label=scales::comma(sum), x=-1*sum), hjust= -0.5) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("#0bf9ea", "#029386")) +
  theme_minimal() +
  labs(x = "", y = "", fill = "Gender", 
       title = "Total Monthly Premium by Marital Status & Gender")
```
  
In total, married customers paid the largest chunk of premium for both male and
female followed by Single customers than divorced customers.Whereas on an average divorced female customers paid more premium than married
and single female customers while married male customers paid more premium than
both single and divorced customers.  
  
<br> 

### Relationship between customer's residence and Premium
##### State
```{r}
num_cat_sumy(data, monthly_premium_auto, state)
num_cat_sumy(data, monthly_premium_auto, state, sumy_fun = sum)
```
  
Total Monthly premium paid is the highest in California followed by Oregon and
Arizona this is boosted by the market share of customers in those state.
While based of the median monthly premium, customers in Nevada paid more premium monthly, which is directly followed by California and Oregon.  
  
  
##### Location Code
```{r}
num_cat_sumy(data, monthly_premium_auto, location_code)
num_cat_sumy(data, monthly_premium_auto, location_code, sumy_fun = sum)
```
  
Given that safe areas pays less premium than area that are known to be unsafe,
the analysis shows that Urban customers pays less premium when looking at the median monthly premium than rural and suburban customers. In essence there is a possibility that the company perceived that Suburban areas are less safe for vehicle than rural and urban areas.
  
  
```{r}
num_cat_sumy2(data, monthly_premium_auto, state, location_code)
```
  
Given the relationship between premium and customer's state above, urban areas
pay less premium than rural and suburban with the exception of Washington 
where customers paid a higher premium in urban areas than rural areas.
  
<br>

### Relationship between vehicle classification and Premium
##### Vehicle class
```{r}
num_cat_dis(data, monthly_premium_auto, vehicle_class, p_typ = "vio")
num_cat_sumy(data, monthly_premium_auto, vehicle_class)
```
  
vehicle known for their higher quality and class cost more premium than 
other classes of vehicles, from the analysis it shows that owners of luxury SUV, luxury cars and sport cars paid more premium on an average than other vehicle class.
  
##### Vehicle size
```{r}
num_cat_dis(data, monthly_premium_auto, vehicle_size, p_typ = "vio")
num_cat_sumy(data, monthly_premium_auto, vehicle_size)
```
  
Customers with midsize vehicles paid more premium on an average than customer
with large vehicles and small vehicles (there is a large segment or customers with midsize vehicles).
    
  
```{r}
num_cat_sumy2(data, monthly_premium_auto, vehicle_size, vehicle_class)
```
  
Given the above analysis on both vehicle class and size, higher quality cars
pays more for all vehicle size with the exception of small size Sport Car which
paid less premium than small size SUV.
  
<br>
Previous [Analysis on Customer Lifetime Values](page_1.html)   
Next [Analysis On Number Of Policies Owned By policyholders](page_3.html)